resevol: an R package for spatially explicit models of pesticide resistance given evolving pest genomes

### 2022-07-16 notebook/ms/ms.Rmd
Write more and finish up the landscape section, move on to pest ecology

Each farm can hold one pesticide and one crop type at any time step, and up to 10 pesticides and 10 crop types are available.

@@

Integrating traits into simulations
===================================================

>>>>

Each farm can hold one pesticide and one crop type at any time step.
The `crop_init` and `pesticide_init` arguments initialise one of `crop_number` crops and one of `pesticide_number` pesticides for each farm, respectively (maximum of 10 each).
Initialisation can be random for each farm with equal probability, or can be set using a vector of length `farms` in which vector elements define the initialised crop or pesticide number.
After initialisation, crops and pesticides rotate once ever `crop_rotation_time` and `pesticide_rotation_time` time steps, respectively.
Each of these rotation time arguments can take either an integer value from 1-3, or a matrix.
Integer values specify (1) no rotation, (2) random transition from one type to another, or (3) cycling through each available crop or pesticide in order.
Square matrices can be used to define the probability that a given crop or pesticide in row $i$ transitions to that in column $j$. 
Hence, any possible Markov chain can be used to transition between crop or pesticide types on farms.

Pest ecology
---------------------------------------------------

Individual pests can be modelled to have several reproductive systems and life histories.

@@

Pest evolution
---------------------------------------------------
